README.md

### 2021-10-23 README.Rmd
updated readme ☘️

This repository stores all the information related to the manuscript *Seed ecology of European mesic meadows*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Data files including the seed trait datasets (European, Iberian and Cantabrian) and the phylogenetic tree.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including figures and models.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.

@@

Please cite the dataset as `CITATION`

>>>>

This repository stores all the information related to the manuscript [*Seed ecology of European mesic meadows*](https://dx.doi.org/10.1093/aob/mcab135), including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Data files including the [European](https://github.com/efernandezpascual/meadows/blob/master/data/european.csv), [Iberian](https://github.com/efernandezpascual/meadows/blob/master/data/iberian.csv) and [Cantabrian](https://github.com/efernandezpascual/meadows/blob/master/data/cantabrian.csv) datasets; the [seed morphometrics](https://github.com/efernandezpascual/meadows/blob/master/data/morphometrics.csv) and the [phylogenetic tree](https://github.com/efernandezpascual/meadows/blob/master/data/meadowstree.tree).
* `doc` Files to create the [manuscript](https://github.com/efernandezpascual/meadows/blob/master/doc/manuscript.md) using `Rmarkdown`.
* `results` Output of the `R` scripts, including figures and models.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.

## Abstract

* **Background and Aims** European mesic meadows are semi-natural open habitats of high biodiversity and an essential part of European landscapes. These species-rich communities can be a source of seed mixes for ecological restoration, urban greening and rewilding. However, limited knowledge of species germination traits is a bottleneck to the development of a competitive native seed industry. Here, we synthesize the seed ecology of mesic meadows.
* **Methods** We combined our own experimental data with data obtained from databases to create a combined dataset containing 2,005 germination records of 90 plant species from 31 European countries. We performed a Bayesian meta-analysis of this dataset to test the seed germination response to environmental cues including scarification, stratification, temperature, alternating temperature and light. We also used multivariate ordination to check the relationship between seed traits (germination and morphology) and species ecological preferences, and to compare the seed ecology of mesic meadows with that of other herbaceous plant communities from the same area.
* **Key Results** The seed ecology of mesic meadows is characterized by (1) high seed germinability when compared to other herbaceous plant communities; (2) low correspondence between seed traits and species ecological preferences; and (3) a deep phylogenetic separation between the two major families, Poaceae and Fabaceae. Poaceae produce many light seeds which respond to gap-detecting germination cues (alternating temperatures and light); Fabaceae produce fewer heavy seeds, which need scarification to break their physical dormancy.
* **Conclusions** High germinability of meadow seeds will reduce their capacity to form persistent seed banks, resulting in dispersal limitations to passive regeneration. For centuries, human activities have shaped the regeneration of meadows, leading to a loss of seed dormancy and decoupling seeds from seasonal cycles, as has been found in many domesticated species. The same anthropic processes that have shaped semi-natural mesic meadows have left them dependent on continued human intervention for their regeneration, highlighting the importance of active restoration via seed supply.

@@

Please cite the repository, datasets and article as:

> Fernández-Pascual E, Vaz M, Morais B, Reiné R, Ascaso J, Afif Khouri E, Carta A. [Seed germination ecology of European mesic meadows.](https://dx.doi.org/10.1093/aob/mcab135) *Annals of Botany*, in press.
